\selectlanguage{english}
\addchap*{Acknowledgments}

First and foremost, I would like to thank my supervisor, Michael Strube. 
It has been an honor for me to be a Ph.D. student of Michael. 
He is a true mentor, who has guided me in how to perform and present fascinating research. 
I appreciate all of his contributions of time, ideas and motivations to make my Ph.D. experience productive and stimulating. 
Moreover, his patient and careful editing of my research papers have considerably improved my skills in scientific writing and presentation. 

I give my gratitude to Anette Frank, Katja Markert, and their team members for their useful comments and questions about my research during my presentations in Ph.D. colloquium series at Heidelberg University.  
I am eternally grateful to Katja Markert for agreeing to be the second reviewer of this thesis. 

Many thanks to the Klaus Tschira Foundation for financially supporting me by a Ph.D.\ scholarship during the time that I was conducting my research at Heidelberg Institute for Theoretical Studies (HITS). 
I appreciate the German Research Foundation as part of research training group “Adaptive Preparation of Information from Heterogeneous Sources” (AIPHES) for supporting me, as one of its associate researchers, to travel to a conference in the U.S. for presenting one of my papers, which is used in the research of this dissertation.   

I want to express my heartfelt gratefulness to all HITS members for providing a friendly and inspiring environment. 
In particular, I thank my colleagues in the natural language processing (NLP) group at HITS:
Alex Judea, Angela Fahrni, Benjamin Heinzerling, Daraksha Parveen, Nafise Moosavi, \mbox{Mark-Christoph} M{\"u}ller, and Sebastian Martschat.  
People who were the first that listened to my research ideas and the last that read my papers before submissions. 

My sincere thanks also go to Holger Gebert, one of the leaders of NLP projects at SAP SE in Germany, and Ashish Gard, the manager of the Siri team at Apple Inc.\ in the U.S., for providing me an opportunity to join their teams as an intern. 
They gave me access to the laboratory and research facilities to deepen my knowledge of NLP and machine learning. 

Last but not least, I want to thank my family and friends, who have always been supportive. 
Individually, my heartfelt thanks are for my spouse Shaghayegh Tavafi for all of her lovely supports in all easy and challenging moments of our residents in Germany. 